---
title: "Heuristic Algorithms for VRP"
author: "Naveen Kaveti"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

We all know about the complexity of VRP algorithms. Getting global optimal routes for a VRP problem is almost impossible even for a smaller number of customer nodes. Even if it is possible we may need to wait for hours to get a global optimal solutions and this may not be possible for most of the business problems. Some time business may require real-time better routes (may not be optimal routes) to service their customers as early as possible. Objective of this package is to implement heuristic algorithms to find greedy routes in almost real-time. Currently implemented Clarke-Wright Savings algorithm, both parallel and sequential methods for CVRP (Capacitated Vehicle Routing Problem). I am planning to implement more features into the problem (like, time-window, backhauls and etc) and more greedy approaches, if possible.

## Clarke-Wright Savings Algorithm

Clarke-Wright Savings is one of the most famous algorithm for VRP problems. The key feature of this algorithm is very less computational time.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
